Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-16 paper/paper.tex
removed unused packages
which font assignment is right? T1 or OT1

\setcopyright{rightsretained}

\usepackage{siunitx}
\usepackage[color]{changebar}
\usepackage{enumitem}
\usepackage[lighttt]{lmodern}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{url}
\usepackage{etoolbox}

@@

\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.839}\ttfamily\small, columns=flexible, showstringspaces=false}
}

@@

\acmConference[IFL 2016]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmYear{2016}
\copyrightyear{2017}

@@

\copyrightyear{2016}
\setcopyright{acmlicensed}
\acmConference[IFL 2016]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmISBN{978-1-4503-4767-9/16/08}
\acmPrice{15.00}
\acmDOI{http://dx.doi.org/10.1145/3064899.3064910}

>>>>

\usepackage{siunitx}
\usepackage[color]{changebar}
\usepackage[lighttt]{lmodern}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{etoolbox}

@@

\setcopyright{acmlicensed}

\ttfamily
\DeclareFontShape{T1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{%
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{%
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.839}\ttfamily\small, columns=flexible, showstringspaces=false}
}%

@@

@@

\copyrightyear{2016}
\acmConference[IFL 2016]{Implementation and Application of Functional Programming Languages}{August 2016}{Leuven, Belgium}
\acmISBN{978-1-4503-4767-9/16/08}
\acmPrice{15.00}
\acmDOI{http://dx.doi.org/10.1145/3064899.3064910}
